\documentclass[
	fontsize=12pt,
    paper=a4,
    pagesize=auto,
    parskip=half,
    titlepage=on,
    ngerman
]{scrartcl}


\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{lmodern}
\usepackage{microtype}

\begin{document}
	
\title{
    NONAMEGAME\\
	Team Or8Bit
}
\subtitle{
  by Fabian Stiewitz, Manuel Jung, Simon Triem
}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Game Design}

\subsection{General Idea}

    Round-based strategy game with 3D view on 2D map. Basic idea from "Battle Isle" with elements of base building and
    event-based major map changes.

\subsection{Details}

  Goal: Two factions enter. One leaves.

\subsection{Map}
  \begin{itemize}
  	\item Map is split up in hexagonal tiles.
  	\item Each tile has a terrain type which modify properties of units on top of it.
  	\item \textit{Version no. 0: Static map with ground and water type}
  	\item \textit{Version no. 1: Static map with plains, sea, river, forest, mountains and hills type.}
  	\item \textit{Version no. 2: Add a large dam (major map event: dam destruction/flooding)}
    \item \textit{Version no. 3: Second map with nuclear plant (major map event: fallout)}
  	\item \textit{Version no. 4: More maps (see Campaign)}
  \end{itemize}

\subsection{Units}
  \begin{itemize}
  	\item Each faction has the same units.
  	\item Different walking distance for each terrain type.
  	\item Different effectiveness for each terrain type.
  	\item Health Points, Defense Points, Attack Points.
  	\item \textit{Version no. 0: One unit type (ground troops)}
  	\item \textit{Version no. 1: Constellation Bonus (taking nearby units into consideration)}
  	\item \textit{Version no. 2: More units}
  \end{itemize}

\subsection {Buildings}
\begin{itemize}
	\item Buildings are static objects on the map.
	\item Gives bonus to whoever owns it.
	\item Gives huge defensive advantage to owning faction.
	\item Some can be built by the player.
	\item Promotion system: Sacrifice a "big" moveable unit (tanks, artillery, idk) for a static defensive building.
	\item \textit{Version no. 0: One building type (base)}
	\item \textit{Version no. 1: Event buildings (see Terrain)}
	\item \textit{Version no. 2: Production plant}
	\item \textit{****** Version no. 3: Promotion system}
\end{itemize}

\section{Menus}

\subsection{Main Menu}
  \begin{itemize}
  	\item  New Game
  	\item Load Game
  	\item Options
  	\begin{itemize}
  	\item  Gameplay
  	\item  Graphics
  	\item  Keys
  	\item  Audio	
  	\end{itemize}
   \item Exit
  \end{itemize}

\subsection{Pause Menu}
  \begin{itemize}
  	\item Continue
  	\item Save Game
  	\item Options (see Main Menu)
  	\item Exit
  \end{itemize}

\section{AI}

\section{technical details}

\subsection{tools}
  \begin{itemize}
  	\item C++ Language
  	\item git
  	\item cmake
  \end{itemize}
\subsection{engine}
  self-developed OpenGL graphics engine
\section{assets}

\section{docs}

\end{document}